---
title: "Explore Provincial Data"
---

##Research Method
In this project, the two hypotheses suggested in the existing studies will be tested by a statistial analysis, with a larger set of data. Statistical analysis complements the existing studies because **it can be used to include the information across the seven different provinces over ten years.** Specifically, in this paper, Shanghai, Shandong, Jiangxi, Hubei, Sichuan, Qinghai, and Guangdong's data from 1992 to 2011 will be included, although most of the provinces do not have the complete yearly data. The provinces and years are selected based on the availability of the data on the frequency of litigation, collected from Law Yearbook of China. Furthermore, among the provinces that have relevant data available, the seven provinces are selected based on their locations, as can be seen from Figure 2. Locations are selected to be evenly distributed across the mainland China in order to prevent dependent variables from being concentrated on certain areas, which would cause bias toward rich/poor or coast/interior regions. With such information, statistical analysis employed in this paper is expected to maximize the generalizability of the results of this research.

In addition, with statistical analysis, **the effect of the economic factor and the education factor will be compared**. By doing so, we can figure out which hypothesis is more persuasive.

Since the data is consisted of province/year observation, **linear regression models for panel data** will be used.

```{r, include = FALSE}
library(shiny)
library(shinythemes)
library(readr)
library(dplyr)

knitr::opts_chunk$set(echo = FALSE)
```

##**The interactive section below lets you explore the dataset for each province.**

```{r}
knitr::include_app("https://jongyoonbaik.shinyapps.io/hw10/", height = 700)
# knitr::include_app("http://127.0.0.1:3203/", height = 400)
```